### 2012-05-18 inst/examples/cost_of_bias.Rmd
cost of bias -- huh? what cost?

```{r}
est_pars <- pars
par_var <- .1
````

@@

```{r}
set.seed(42)
bias <- rnorm(100, pars[1], par_var)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- bias[i]
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r}
require(snowfall)
sfInit(parallel=T, cpu=16)
sfLibrary(pdgControl)
sfExportAll()
sims_four <- sfLapply(1:100, function(i){
  est_pars[1] <- bias[i] 
  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r echo=TRUE}
setkey(dt, uncertainty)
cost_of_bias = dt[knownBias, sum(profit), by=reps]$V1 - dt[randomBias, sum(profit), by=reps]$V1
cost_of_bias
mean(cost_of_bias)
sd(cost_of_bias)
````

>>>>

```{r}
est_pars <- pars
par_var <- .2
````

@@

```{r}
bias <- rnorm(100, pars[1], par_var)
set.seed(42)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- bias[i]
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

For the record, the biases by index number are:

```{r }
bias
````

@@

```{r}
#require(snowfall)
#sfInit(parallel=T, cpu=16)
#sfLibrary(pdgControl)
#sfExportAll()
set.seed(42)
sims_four <- lapply(1:100, function(i){
  est_pars[1] <- bias[i] 
  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r echo=TRUE}
setkey(dt, uncertainty)
cost_of_bias = dt[uncertainty=="KnownBias", sum(profit), by=reps]$V1 - dt[uncertainty=="RandomBias", sum(profit), by=reps]$V1
cost_of_bias
mean(cost_of_bias)
sd(cost_of_bias)
````
